---
title: "STAT 331 Portfolio"
author: "Paco Jones"
format: html 
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an A-.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1

```{r}
#| label: wd-1-csv-1

# Lab 4 Problem 0

childcare_costs <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/childcare_costs.csv')

counties <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/counties.csv')

tax_rev <- read_csv('https://atheobold.github.io/groupworthy-data-science/labs/instructions/data/ca_tax_revenue.csv')
```

-   `csv` Example 2

```{r}
#| label: wd-1-csv-2

# Lab 3 Problem 2

teacher_evals <- read_csv(here::here("Week 3", "Lab 3", "teacher_evals.csv"))

```

-   `xlsx`

```{r}
#| label: wd-1-xlsx

# Practice Activity 4 -- Group Submission #1

library(tidyverse)
library(readxl)
military <- read_xlsx("gov_spending_per_capita.xlsx",
                      sheet = "Share of Govt. spending" ,
                      skip  = 7,
                      n_max = 190,
                      na = c("xxx", ". .", "..")
                      )
military

```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns

```{r}
#| label: wd-2-ex-1

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   Example removing specified columns

```{r}
#| label: wd-2-ex-2

# Lab 9 Problem 6

evals |>
  select(teacher_id, academic_degree, seniority, sex) |>
  distinct(teacher_id, .keep_all = TRUE) |>
  mutate(
    seniority = if_else(seniority <= 4, "junior", "senior")
  ) |>
  select(-teacher_id) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "level"
  ) |>
  count(variable, level) |>
  group_by(variable) |>
  mutate(prop = n / sum(n)) |>
  ungroup() |>
  mutate(
    level = case_match(
      level,
      "not_tenured" ~ "No Degree",
      "no_dgr" ~ "No Degree",
      "tenured" ~ "Tenured Professor",
      "prof" ~ "Tenured Professor",
      "dr" ~ "Doctorate",
      "ma" ~ "Masters",
      .default = str_to_title(str_replace_all(level, "_", " "))
    ),
    variable = str_replace_all(variable, "_", " "),
    variable = str_to_title(variable)
  ) |>
  gt(groupname_col = "variable") |>
  tab_header(
    title = "Demographics of Professors",
    subtitle = "Student Evaluations at the University of Poland, Warsaw in 2020"
  ) |>
  cols_label(
    level = "Demographic",
    n = "Count",
    prop = "%"
  ) |>
  tab_spanner(
    label = "Professors",
    columns = c(n, prop)
  ) |>
  fmt_percent(
    columns = prop,
    decimals = 2
  ) |>
  tab_options(
    row_group.font.weight = "bold",
    row_group.background.color = "#E8E8E8"
  )
```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`)

```{r}
#| label: wd-2-ex-3

# Lab 3 Problem 5 Revised
# Changed from selecting 10 columns to removing the columns not used, and from # across(c(teacher_id, course_id), as.character) to 
# across(.cols = c(teacher_id, course_id), .fns  = ~ as.character(.x))


teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(.cols = c(teacher_id, course_id),
       .fns  = ~ as.character(.x)),
         across(.cols = c(question_no, academic_degree, sex),
       .fns  = ~ as.factor(.x))
  ) %>%
  select(-c(starts_with("stud"), percent_failed, class_duration, weekday, time_of_day, SET_score_1sem, maximum_score))

teacher_evals_clean
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-3-numeric-ex-1

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

-   Numeric Example 2

```{r}
#| label: wd-3-numeric-ex-1

# Lab 3 Question 5

teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(c(teacher_id, course_id), as.character),
         across(c(question_no, academic_degree, sex), as.factor)
  ) %>%
  select(course_id, teacher_id, question_no, no_participants, resp_share,
         SET_score_avg, percent_failed_cur, academic_degree, seniority, sex)
teacher_evals_clean

```

-   Character Example 1 (any context)

```{r}
#| label: wd-3-character

# Lab 4 Problem 2

ca_childcare <- counties %>%
  filter(state_name == "California") %>%
  inner_join(childcare_costs, by = "county_fips_code")

ca_childcare

```

-   Character Example 2 (example must use functions from **stringr**)

```{r}
#| label: wd-3-string

# Lab 5 Access Report from Date of Murder Revised
# From my original version, I changed the date variable from numeric to date-time and then adjusted the filter to account for that

crime_scene_report %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
  filter(type == "murder",
         date == as.Date("2018-01-15"),
         city == "SQL City")
```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-3-date

# Lab 5 Access Report from Date of Murder Revised
# From my original version, I changed the date variable from numeric to date-time and then adjusted the filter to account for that

crime_scene_report %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
  filter(type == "murder",
         date == as.Date("2018-01-15"),
         city == "SQL City")
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-4-numeric-ex-1

# Challenge 3 Problem 1

teacher_evals_compare <- teacher_evals %>%
  filter(question_no == 903) %>%
  mutate(
    set_level = if_else(SET_score_avg >= 4, "excellent", "standard"),
    sen_level = case_when(
      seniority <= 4 ~ "junior",
      seniority <= 8 ~ "senior",
      seniority > 8 ~ "very senior"
    )
  ) %>%
  select(course_id, set_level, sen_level)

teacher_evals_compare
```

-   Numeric Example 2

```{r}
#| label: wd-4-numeric-ex-2

# Lab 9 Problem 5

evals |>
  select(teacher_id, academic_degree, seniority, sex) |>
  distinct(teacher_id, .keep_all = TRUE) |>
  mutate(
    seniority = if_else(seniority <= 4, "junior", "senior")
  ) |>
  select(-teacher_id) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "level"
  ) |>
  count(variable, level) |>
  group_by(variable) |>
  mutate(prop = n / sum(n)) |>
  ungroup() |>
  mutate(
    level = case_match(
      level,
      "no_dgr" ~ "No Degree",
      "prof" ~ "Tenured Professor",
      "dr" ~ "Doctorate",
      "ma" ~ "Masters",
      .default = str_to_title(str_replace_all(level, "_", " "))
    ),
    variable = str_replace_all(variable, "_", " "),
    variable = str_to_title(variable)
  )  |>
  kable() |>
  kable_styling(full_width = FALSE, bootstrap_options = "striped") |>
  row_spec(0, bold = TRUE)
```

-   Factor Example 1 (renaming levels)

```{r}
#| label: wd-4-factor-ex-1

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   Factor Example 2 (reordering levels)

```{r}
#| label: wd-4-factor-ex-2

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )
```

-   Character (example must use functions from **stringr**)

```{r}
#| label: wd-4-string

# Lab 3 Problem 5 Revised
# Changed from selecting 10 columns to removing the columns not used, and from # across(c(teacher_id, course_id), as.character) to 
# across(.cols = c(teacher_id, course_id), .fns  = ~ as.character(.x))


teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(.cols = c(teacher_id, course_id),
       .fns  = ~ as.character(.x)),
         across(.cols = c(question_no, academic_degree, sex),
       .fns  = ~ as.factor(.x))
  ) %>%
  select(-c(starts_with("stud"), percent_failed, class_duration, weekday, time_of_day, SET_score_1sem, maximum_score))

teacher_evals_clean
```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-4-date

# Lab 5 Access Report from Date of Murder Revised
# From my original version, I changed the date variable from numeric to date-time and then adjusted the filter to account for that

crime_scene_report %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
  filter(type == "murder",
         date == as.Date("2018-01-15"),
         city == "SQL City")
```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1

```{r}
#| label: wd-5-left-ex-1

# Lab 4 Problem 3

ca_childcare <- ca_childcare %>%
  left_join(tax_rev, 
             by = c("county_name" = "entity_name", 
                    "study_year" = "year"))

ca_childcare
```

-   `right_join()` Example 1

```{r}
#| label: wd-5-right

# Lab 4 Problem 3 Revised
# Changed from left_join to right_join

ca_childcare <- tax_rev %>%
  right_join(
    ca_childcare,
    by = c("entity_name" = "county_name",
           "year" = "study_year")
  )

ca_childcare
```

-   `left_join()` **or** `right_join()` Example 2

```{r}
#| label: wd-5-left-right-ex-2

```

-   `inner_join()` Example 1

```{r}
#| label: wd-5-inner-ex-1

# Lab 4 Problem 2

ca_childcare <- counties %>%
  filter(state_name == "California") %>%
  inner_join(childcare_costs, by = "county_fips_code")

ca_childcare
```

-   `inner_join()` Example 2

```{r}
#| label: wd-5-inner-ex-2

# Lab 5 Find interviews from two witnesses revised
# Changed from filtering person and interview separately to using an inner_join to filter them in one pipe

witness_interviews <- person %>%
  group_by(address_street_name) %>%
  filter(
    # last house on Northwestern Dr
    (address_street_name == "Northwestern Dr" &
       address_number == max(address_number)) |
      # Annabel on Franklin Ave
      (address_street_name == "Franklin Ave" &
         str_detect(name, "Annabel"))
  ) %>%
  ungroup() %>%
  inner_join(interview, by = c("id" = "person_id"))

witness_interviews
```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r}
#| label: wd-6-semi

```

-   `anti_join()`

```{r}
#| label: wd-6-anti

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r}
#| label: wd-7-long

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   `pivot_wider()`

```{r}
#| label: wd-7-wide

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Example 1: Challenge 2
-   Example 2: Lab 2
-   Example 3: Lab 3
-   Example 4: Lab 7
-   Example 5: Lab 9

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting

```{r}
#| label: r-2-1

# Lab 4 Problem 8 Revised
# Changed dollar_format() to label_dollar()

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::label_dollar()) +
  scale_y_continuous(labels = scales::label_dollar())
```

-   Example of **dplyr** pipeline

```{r}
#| label: r-2-2

# Lab 4 Problem 6

ca_childcare %>%
  filter(study_year == 2018) %>%
  group_by(census_region) %>%
  summarize(median_mc_infant = median(mc_infant), .groups = "drop") %>%
  slice_min(median_mc_infant, n = 1)

```

-   Example of function formatting

```{r}
#| label: r-2-3

# Lab 8 Problem 2

pivot_table <- function(df, row_var, col_var) {
  
  df %>%
    count({{ row_var}}, {{ col_var }}) %>%
    pivot_wider(
      names_from = {{ col_var }},
      values_from = n,
      values_fill = 0
    ) %>%
    adorn_totals(where = c("row", "col"))

}
```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context)

```{r}
#| label: r-3-example

# Lab 8 Problem 4

style_plot <- function(p,
                       theme_fn = theme_minimal,
                       palette  = brewer.pal(8, "Set2"),
                       aesthetic = "fill") {
  
  stopifnot(aesthetic %in% c("fill", "color"))
  
  p <- p + theme_fn()

  if (aesthetic == "fill") {
    p <- p + scale_fill_manual(values = palette)
  } else {
    p <- p + scale_color_manual(values = palette)
  }

  p
}
```

-   Example (function stops)

```{r}
#| label: r-3-function-stops

# Lab 7 Problem 4 Revised
# Changed from return(rescaled) to rescaled

rescale_01 <- function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric.")
  }
  if (length(x) <= 1) {
    stop("Input vector must have length greater than 1.")
  }

  rng <- range(x, na.rm = TRUE)
  rescaled <- (x - rng[1]) / (rng[2] - rng[1])
  
  rescaled
}
```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables

```{r}
#| label: dvs-1-num

# Lab 4 Problem 8 Revised
# Changed dollar_format() to label_dollar()

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::label_dollar()) +
  scale_y_continuous(labels = scales::label_dollar())

```

-   At least one numeric variable and one categorical variable

```{r}
#| label: dvs-2-num-cat

# Lab 2 Problem 16

ggplot(data = surveys, aes(x = weight, y = species)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(height = 0.2, color = "steelblue", alpha = 0.3) +
  labs(
    x = "Weight (g)",
    y = "Species",
    title = "Distribution of Weight by Species (Flipped)"
  )

```

-   At least two categorical variables

```{r}
#| label: dvs-2-cat

# Challenge 3 Problem 2 Revised
# Changed percent to label_percent() and y label from count to Proportion

ggplot(teacher_evals_compare, aes(x = sen_level, fill = set_level)) +
  geom_bar(position = "fill", color = "white") +
  scale_y_continuous(labels = scales::label_percent()) +
  scale_fill_manual(values = c("excellent" = "purple", "standard" = "tan")) +
  labs(
    title = "Evaluation of Teachers' Use of Activities",
    x = "Years of Experience",
    y = 'Proportion',
    fill = "Evaluation Rating"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(),
    legend.position = "top",
    legend.title = element_text()
  )
```

-   Dates (time series plot)

```{r}
#| label: dvs-2-date

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )
```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable

```{r}
#| label: dvs-2-ex-1

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   I can modify my colors to be accessible to anyone's eyes

```{r}
#| label: dvs-2-ex-2

# Lab 8 Problem 4

style_plot <- function(p,
                       theme_fn = theme_minimal,
                       palette  = brewer.pal(8, "Set2"),
                       aesthetic = "fill") {
  
  stopifnot(aesthetic %in% c("fill", "color"))
  
  p <- p + theme_fn()

  if (aesthetic == "fill") {
    p <- p + scale_fill_manual(values = palette)
  } else {
    p <- p + scale_color_manual(values = palette)
  }

  p
}

my_plot <- ggplot(penguins, mapping = aes(x = species, fill = sex)) + 
  geom_bar()

style_plot(my_plot, 
           theme_fn = theme_bw, 
           palette = brewer.pal(3, "Paired"), 
           aesthetic = "fill")
```

-   I can modify my plot titles to clearly communicate the data context

```{r}
#| label: dvs-2-ex-3

# Lab 4 Problem 8 Revised
# Changed dollar_format() to label_dollar()

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::label_dollar()) +
  scale_y_continuous(labels = scales::label_dollar())

```

-   I can modify the text in my plot to be more readable

```{r}
#| label: dvs-2-ex-4

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   I can reorder my legend to align with the colors in my plot

```{r}
#| label: dvs-2-ex-5

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )
```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1)

```{r}
#| label: dvs-3-1-ex-1

# Challenge 2 Medium: Exploring Colors

library(viridis)

ggplot(data = surveys, aes(x = weight, y = species, fill = sex)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_jitter(aes(color = sex), position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.8), alpha = 0.05) +
  scale_color_viridis_d(option = "plasma", begin = 0.2, end = 0.8) +
  labs(
    x = "Weight (g)",
    y = "Species",
    title = "Distribution of Weight by Species and Sex (Flipped, Colored by Sex)"
  )

```

-   I can use non-standard colors (Example 2)

```{r}
#| label: dvs-3-1-ex-2

# Lab 8 Problem 4

style_plot <- function(p,
                       theme_fn = theme_minimal,
                       palette  = brewer.pal(8, "Set2"),
                       aesthetic = "fill") {
  
  stopifnot(aesthetic %in% c("fill", "color"))
  
  p <- p + theme_fn()

  if (aesthetic == "fill") {
    p <- p + scale_fill_manual(values = palette)
  } else {
    p <- p + scale_color_manual(values = palette)
  }

  p
}

my_plot <- ggplot(penguins, mapping = aes(x = species, fill = sex)) + 
  geom_bar()

style_plot(my_plot, 
           theme_fn = theme_bw, 
           palette = brewer.pal(3, "Paired"), 
           aesthetic = "fill")
```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

# Lab 7 Problem 3 Revised
# Changed size from 3 to 4 and color to white inside geom_text()

fish %>%
  mutate(.row_has_na = if_any(everything(), is.na)) %>%
  group_by(year, section, trip) %>%
  summarize(
    missing_count = sum(.row_has_na),
    total = n(),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = section, y = factor(year), fill = missing_count)) +
  geom_tile(color = "white") +
  geom_text(aes(label = missing_count), size = 4, color = "white") +
  facet_wrap(~ trip, labeller = label_both) +
  scale_fill_viridis_c(option = "plasma") +
  labs(
    title = "Missing Value Counts by Year, Section, and Trip",
    x = "Section",
    y = "Year",
    fill = "Missing Count"
  ) +
  theme_minimal(base_size = 12)
```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

# Lab 10 Problem 13

set.seed(111)

ci_dat %>%
  sample_n(100) %>%
  mutate(
    id = row_number(),
    misses = cover == 0,
    beta1_true = 0.5
  ) %>%
  ggplot(aes(y = id, x = estimate)) +
    geom_errorbar(
      aes(xmin = conf.low, xmax = conf.high, color = misses),
      height = 0.2, linewidth = 0.9
    ) +
    geom_vline(aes(xintercept = beta1_true), linetype = "dashed") +
    scale_color_manual(values = c("FALSE" = "skyblue", "TRUE" = "red")) +
    labs(
      title = "95% Confidence Intervals of Estimated Regression Slope\nfor 100 Simulated Datasets",
      subtitle = "Intervals that miss the true population slope are shown in red",
      x = "Slope Coefficient Estimate",
      y = "Simulation Index"
    ) +
    theme_minimal()
```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()`

```{r}
#| label: dvs-4-summarize

# Lab 7 Problem 1

missing_summary <- fish %>%
  summarize(
    observations_with_missing = sum(if_any(everything(), is.na)),
    across(everything(), ~ sum(is.na(.)))
  )

missing_summary
```

-   Example using `across()`

```{r}
#| label: dvs-4-across

# Lab 7 Problem 1

missing_summary <- fish %>%
  summarize(
    observations_with_missing = sum(if_any(everything(), is.na)),
    across(everything(), ~ sum(is.na(.)))
  )

missing_summary
```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r}
#| label: dvs-5-16

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))
```

-   Example 2

```{r}
#| label: dvs-5-2

# Lab 3 Problem 10

teacher_evals_clean %>%
  filter(question_no == 901) %>%
  group_by(teacher_id) %>%
  summarize(
    n_courses = n_distinct(course_id),
    avg_q1_score = mean(SET_score_avg)
  ) %>%
  filter(n_courses >= 5) %>%
  ungroup() %>%
  filter(avg_q1_score == max(avg_q1_score) | avg_q1_score == min(avg_q1_score))

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context

```{r}
#| label: dvs-6-ex-1

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers)

```{r}
#| label: dvs-6-ex-2

# Lab 9 Problem 3

surveys |>
  map_chr(class) |>
  enframe(name = "Variable", value = "Data Type") |>
  mutate(`Data Type` = str_to_lower(`Data Type`)) |>
  arrange(`Data Type`) |>
  kable(
    caption = "Each variable describes some aspect of a single animal observation recorded on a given date and plot in the Portal Project."
  ) |>
  row_spec(0, bold = TRUE)
```

-   I can arrange my table to have an intuitive ordering

```{r}
#| label: dvs-6-ex-3

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors

```{r}
#| label: dvs-7-ex-1

# Lab 9 Problem 8

fish |>
  map_int(~ sum(is.na(.))) |>
  enframe(name = "Measurement Variable", value = "Missing Values") |>
  arrange(`Missing Values`) |>
  gt() |>
  tab_header(
    title = "Number of Missing Values for Fish Measurements",
    subtitle = "Data Collected from 1989 to 2006 on the Blackfoot Fish River in Montana"
  ) |>
  data_color(
    columns = `Missing Values`,
    fn = function(x) {
      ifelse(x == 0, "#2A9D8F", "#E76F51")
    }
  )
```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`)

```{r}
#| label: dvs-7-ex-2

# Lab 9 Problem 5

evals |>
  select(teacher_id, academic_degree, seniority, sex) |>
  distinct(teacher_id, .keep_all = TRUE) |>
  mutate(
    seniority = if_else(seniority <= 4, "junior", "senior")
  ) |>
  select(-teacher_id) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "level"
  ) |>
  count(variable, level) |>
  group_by(variable) |>
  mutate(prop = n / sum(n)) |>
  ungroup() |>
  mutate(
    level = case_match(
      level,
      "no_dgr" ~ "No Degree",
      "prof" ~ "Tenured Professor",
      "dr" ~ "Doctorate",
      "ma" ~ "Masters",
      .default = str_to_title(str_replace_all(level, "_", " "))
    ),
    variable = str_replace_all(variable, "_", " "),
    variable = str_to_title(variable)
  )  |>
  kable() |>
  kable_styling(full_width = FALSE, bootstrap_options = "striped") |>
  row_spec(0, bold = TRUE)

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls)

```{r}
#| label: pe-1-one-call

# Lab 8 Problem 4

style_plot <- function(p,
                       theme_fn = theme_minimal,
                       palette  = brewer.pal(8, "Set2"),
                       aesthetic = "fill") {
  
  stopifnot(aesthetic %in% c("fill", "color"))
  
  p <- p + theme_fn()

  if (aesthetic == "fill") {
    p <- p + scale_fill_manual(values = palette)
  } else {
    p <- p + scale_color_manual(values = palette)
  }

  p
}

my_plot <- ggplot(penguins, mapping = aes(x = species, fill = sex)) + 
  geom_bar()

style_plot(my_plot, 
           theme_fn = theme_bw, 
           palette = brewer.pal(3, "Paired"), 
           aesthetic = "fill")
```

-   using `across()`

```{r}
#| label: pe-1-across

# Lab 3 Problem 5 Revised
# Changed from selecting 10 columns to removing the columns not used, and from # across(c(teacher_id, course_id), as.character) to 
# across(.cols = c(teacher_id, course_id), .fns  = ~ as.character(.x))


teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(.cols = c(teacher_id, course_id),
       .fns  = ~ as.character(.x)),
         across(.cols = c(question_no, academic_degree, sex),
       .fns  = ~ as.factor(.x))
  ) %>%
  select(-c(starts_with("stud"), percent_failed, class_duration, weekday, time_of_day, SET_score_1sem, maximum_score))

teacher_evals_clean

```

-   using functions from the `map()` family

```{r}
#| label: pe-1-map-1

# Lab 9 Problem 8

fish |>
  map_int(~ sum(is.na(.))) |>
  enframe(name = "Measurement Variable", value = "Missing Values") |>
  arrange(`Missing Values`) |>
  gt() |>
  tab_header(
    title = "Number of Missing Values for Fish Measurements",
    subtitle = "Data Collected from 1989 to 2006 on the Blackfoot Fish River in Montana"
  ) |>
  data_color(
    columns = `Missing Values`,
    fn = function(x) {
      ifelse(x == 0, "#2A9D8F", "#E76F51")
    }
  )
```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors

```{r}
#| label: pe-2-1

# Lab 7 Problem 4

rescale_01 <- function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric.")
  }
  if (length(x) <= 1) {
    stop("Input vector must have length greater than 1.")
  }

  rng <- range(x, na.rm = TRUE)
  rescaled <- (x - rng[1]) / (rng[2] - rng[1])
  
  return(rescaled)
}
```

-   Example 2: Function that operates on data frames

```{r}
#| label: pe-2-2

# Lab 8 Problem 1 Revised
# Added an input check for a data frame, and added the ~ and .x

rescale_01 <- function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric.")
  }
  if (length(x) <= 1) {
    stop("Input vector must have length greater than 1.")
  }

  rng <- range(x, na.rm = TRUE)
  rescaled <- (x - rng[1]) / (rng[2] - rng[1])
  
  return(rescaled)
}

rescale_column <- function(df, cols) {
  if (!is.data.frame(df)) {
    stop("`df` must be a data frame.")
  }

  df %>%
    mutate(
      across(
        .cols = {{ cols }},
        .fns  = ~ rescale_01(.x)
      )
    )
}
```

-   Example 3: Function that operates on vectors *or* data frames

```{r}
#| label: pe-2-3

# Lab 8 Problem 2 Revised
# Added an input check for a data frame

pivot_table <- function(df, row_var, col_var) {
  if (!is.data.frame(df)) {
    stop("`df` must be a data frame.")
  }
  df %>%
    count({{ row_var }}, {{ col_var }}) %>%
    pivot_wider(
      names_from = {{ col_var}},
      values_from = n,
      values_fill = 0
    ) %>%
    adorn_totals(where = c("row", "col"))

}
```

**PE-3:I can use iteration to reduce repetition in my code.**

-   using `across()`

```{r}
#| label: pe-3-across

# Lab 8 Problem 1 Revised
# Added an input check for a data frame, and added the ~ and .x

rescale_01 <- function(x) {
  if (!is.numeric(x)) {
    stop("Input must be numeric.")
  }
  if (length(x) <= 1) {
    stop("Input vector must have length greater than 1.")
  }

  rng <- range(x, na.rm = TRUE)
  rescaled <- (x - rng[1]) / (rng[2] - rng[1])
  
  return(rescaled)
}

rescale_column <- function(df, cols) {
  if (!is.data.frame(df)) {
    stop("`df` must be a data frame.")
  }

  df %>%
    mutate(
      across(
        .cols = {{ cols }},
        .fns  = ~ rescale_01(.x)
      )
    )
}
```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)

```{r}
#| label: pe-3-map-1

# Lab 10 Problem 10

set.seed(123)

ci_dat <- map(.x = 1:1000,
              .f = ~ mycifun(beta0 = 3, beta1 = 0.5, n = 100)
              )
```

-   using a `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)

```{r}
#| label: pe-3-map-2

# Lab 9 Problem 4

evals <- evals |>
  map_if(is.character, as.factor) |>
  bind_cols()
```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated

```{r}
#| label: pe-4-1

# Lab 8 Problem 2 Revised
# Added an input check for a data frame

pivot_table <- function(df, row_var, col_var) {
  if (!is.data.frame(df)) {
    stop("`df` must be a data frame.")
  }
  df %>%
    count({{ row_var }}, {{ col_var }}) %>%
    pivot_wider(
      names_from = {{ col_var}},
      values_from = n,
      values_fill = 0
    ) %>%
    adorn_totals(where = c("row", "col"))

}

```

-   I can connect a data wrangling pipeline into a `ggplot()`

```{r}
#| label: pe-4-2

# Lab 4 Problem 7 Revised
# Changed from using factor to fct_recode, and fct_reorder to fct_reorder2

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = age_group |>
      fct_recode(
        Infant   = "mc_infant",
        Toddler  = "mc_toddler",
        Preschool = "mc_preschool"
      ) |>
      fct_relevel("Infant", "Toddler", "Preschool"),
    census_region = fct_reorder2(census_region, study_year, median_price)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

## Data Simulation & Statisical Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r}
#| label: dsm-1-1

# Lab 10 Problem 4

# define slope and intercept parameters
intercept = 2
slope = 1

# generate x vector
x <- runif(100, min = 0, max = 1)

# generate noise `ep` vector
ep <- rnorm(100, mean = 0, sd = 1)

# generate outcome from population model
y = intercept + x*slope + ep


# create an "observed data" dataframe with only the x and y vectors
observed_data <- data.frame(x = x, y = y)
```

-   Example 2

```{r}
#| label: dsm-1-2

# Lab 10 Problem 1

randomBabies <- function(n_babies){
  babies <- 1:n_babies
  shuffled <- sample(babies)
  sum(shuffled == babies)
}

set.seed(111)

results <- map_int(.x = 1:10000,
                   .f = ~randomBabies(4)
                  )
```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1

```{r}
#| label: dsm-2-1

# Lab 4 Problem 9

reg_mod1 <- lm(mc_infant ~ mhi_2018, data = ca_childcare)
summary(reg_mod1)

```

-   Example 2

```{r}
#| label: dsm-2-2

# Lab 2 Problem 17

species_mod <- aov(weight ~ species, data = surveys)
summary(species_mod)

```

-   Example 3

```{r}
#| label: dsm-2-3

# Lab 1 Problem 10

t.test(len ~ supp,       
       data = ToothGrowth,
       var.equal = FALSE,  
       alternative = "two.sided")
```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

<!-- For the revisions included in your Portfolio, to help me understand the nature of your revisions, please denote somehow the feedback I provided you (e.g., boldface, italics, colored text) before your revisions. -->

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

## Peer Support & Collaboration

<!-- Include an image or a description of feedback you gave that you are proud of (either in a peer review or in Discord). -->

Your code is overall very clear and thoughtfully structured, and I like how consistently you use pipes to make each step easy to follow. Your pipelines are especially tidy and the use of line breaks and indentation makes the logic visually clean and readable. One way you could improvement is by adding consistent whitespace around arithmetic operators ( x \* slope instead of x\*slope), which would make your code even more tidy. I also noticed a couple instances where you repeat the same data-wrangling steps (such as computing the results summary twice), and consolidating these into a single object would make your code more efficient. But overall your code is very tidy and efficient!

<!-- Include a description of how you grew as a collaborator through the weekly pair programming activities.   -->

I felt like I grew tremendously as a teammate and collaborator throughout the quarter via the weekly pair programming activities. At the start of the quarter, as the computer, I had a difficult time resisting giving my own input or just coding what I thought was best. I also made a lot of assumptions on what the communicator wanted, which were often incorrect. By the end of the quarter, however, I improved greatly at following exactly the instructions of my teammate and clarifying assumptions before typing them in code. These activities helped build my patience, listening skills, and collaborative skills, contrasting from my do-it-myself mentality that I had coming into the class.
