---
title: "STAT 331 Portfolio"
author: "Paco Jones"
format: html 
embed-resources: true
layout: margin-left
editor: visual
execute: 
  eval: false
  echo: true
---

[**My Grade:**]{.underline} I believe my grade equivalent to course work evidenced below to be an \_\_.

[**Learning Objective Evidence:**]{.underline} In the code chunks below, provide code from Lab or Challenge assignments where you believe you have demonstrated proficiency with the specified learning target. Be sure to specify **where** the code came from (e.g., Lab 4 Question 2).

## Working with Data

**WD-1: I can import data from a *variety* of formats (e.g., csv, xlsx, txt, etc.).**

-   `csv` Example 1

```{r}
#| label: wd-1-csv-1

# Lab 4 Problem 0

childcare_costs <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/childcare_costs.csv')

counties <- read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-05-09/counties.csv')

tax_rev <- read_csv('https://atheobold.github.io/groupworthy-data-science/labs/instructions/data/ca_tax_revenue.csv')
```

-   `csv` Example 2

```{r}
#| label: wd-1-csv-2

# Lab 3 Problem 2

teacher_evals <- read_csv(here::here("Week 3", "Lab 3", "teacher_evals.csv"))

```

-   `xlsx`

```{r}
#| label: wd-1-xlsx

# Practice Activity 4 -- Group Submission #1

library(tidyverse)
library(readxl)
military <- read_xlsx("gov_spending_per_capita.xlsx",
                      sheet = "Share of Govt. spending" ,
                      skip  = 7,
                      n_max = 190,
                      na = c("xxx", ". .", "..")
                      )
military

```

**WD-2: I can select necessary columns from a dataset.**

-   Example selecting specified columns

```{r}
#| label: wd-2-ex-1

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   Example removing specified columns

```{r}
#| label: wd-2-ex-2

# Lab 9 Problem 6

evals |>
  select(teacher_id, academic_degree, seniority, sex) |>
  distinct(teacher_id, .keep_all = TRUE) |>
  mutate(
    seniority = if_else(seniority <= 4, "junior", "senior")
  ) |>
  select(-teacher_id) |>
  pivot_longer(
    cols = everything(),
    names_to = "variable",
    values_to = "level"
  ) |>
  count(variable, level) |>
  group_by(variable) |>
  mutate(prop = n / sum(n)) |>
  ungroup() |>
  mutate(
    level = case_match(
      level,
      "not_tenured" ~ "No Degree",
      "no_dgr" ~ "No Degree",
      "tenured" ~ "Tenured Professor",
      "prof" ~ "Tenured Professor",
      "dr" ~ "Doctorate",
      "ma" ~ "Masters",
      .default = str_to_title(str_replace_all(level, "_", " "))
    ),
    variable = str_replace_all(variable, "_", " "),
    variable = str_to_title(variable)
  ) |>
  gt(groupname_col = "variable") |>
  tab_header(
    title = "Demographics of Professors",
    subtitle = "Student Evaluations at the University of Poland, Warsaw in 2020"
  ) |>
  cols_label(
    level = "Demographic",
    n = "Count",
    prop = "%"
  ) |>
  tab_spanner(
    label = "Professors",
    columns = c(n, prop)
  ) |>
  fmt_percent(
    columns = prop,
    decimals = 2
  ) |>
  tab_options(
    row_group.font.weight = "bold",
    row_group.background.color = "#E8E8E8"
  )
```

-   Example selecting columns based on logical values (e.g., `starts_with()`, `ends_with()`, `contains()`, `where()`)

```{r}
#| label: wd-2-ex-3

# Lab 3 Problem 5 Revised
# Changed from selecting 10 columns to removing the columns not used

teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(c(teacher_id, course_id), as.character),
         across(c(question_no, academic_degree, sex), as.factor)
  ) %>%
  select(-c(starts_with("stud"), percent_failed, class_duration, weekday, time_of_day, SET_score_1sem, maximum_score))

teacher_evals_clean
```

**WD-3: I can filter rows from a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-3-numeric-ex-1

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

-   Numeric Example 2

```{r}
#| label: wd-3-numeric-ex-1

# Lab 3 Question 5

teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(c(teacher_id, course_id), as.character),
         across(c(question_no, academic_degree, sex), as.factor)
  ) %>%
  select(course_id, teacher_id, question_no, no_participants, resp_share,
         SET_score_avg, percent_failed_cur, academic_degree, seniority, sex)
teacher_evals_clean

```

-   Character Example 1 (any context)

```{r}
#| label: wd-3-character

# Lab 4 Problem 2

ca_childcare <- counties %>%
  filter(state_name == "California") %>%
  inner_join(childcare_costs, by = "county_fips_code")

ca_childcare

```

-   Character Example 2 (example must use functions from **stringr**)

```{r}
#| label: wd-3-string

# Lab 5 Access Report from Date of Murder Revised
# From my original version, I changed the date variable from numeric to date-time and then adjusted the filter to account for that

crime_scene_report %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
  filter(type == "murder",
         date == as.Date("2018-01-15"),
         city == "SQL City")
```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-3-date

# Lab 5 Access Report from Date of Murder Revised
# From my original version, I changed the date variable from numeric to date-time and then adjusted the filter to account for that

crime_scene_report %>%
  mutate(date = as.Date(as.character(date), format = "%Y%m%d")) %>%
  filter(type == "murder",
         date == as.Date("2018-01-15"),
         city == "SQL City")
```

**WD-4: I can modify existing variables and create new variables in a dataframe for a *variety* of data types (e.g., numeric, integer, character, factor, date).**

-   Numeric Example 1

```{r}
#| label: wd-4-numeric-ex-1


```

-   Numeric Example 2

```{r}
#| label: wd-4-numeric-ex-2

```

-   Factor Example 1 (renaming levels)

```{r}
#| label: wd-4-factor-ex-1

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   Factor Example 2 (reordering levels)

```{r}
#| label: wd-4-factor-ex-2

```

-   Character (example must use functions from **stringr**)

```{r}
#| label: wd-4-string

```

-   Date (example must use functions from **lubridate**)

```{r}
#| label: wd-4-date

```

**WD-5: I can use mutating joins to combine multiple dataframes.**

-   `left_join()` Example 1

```{r}
#| label: wd-5-left-ex-1

# Lab 4 Problem 3

ca_childcare <- ca_childcare %>%
  left_join(tax_rev, 
             by = c("county_name" = "entity_name", 
                    "study_year" = "year"))

ca_childcare
```

-   `right_join()` Example 1

```{r}
#| label: wd-5-right

```

-   `left_join()` **or** `right_join()` Example 2

```{r}
#| label: wd-5-left-right-ex-2

```

-   `inner_join()` Example 1

```{r}
#| label: wd-5-inner-ex-1

# Lab 4 Problem 2

ca_childcare <- counties %>%
  filter(state_name == "California") %>%
  inner_join(childcare_costs, by = "county_fips_code")

ca_childcare
```

-   `inner_join()` Example 2

```{r}
#| label: wd-5-inner-ex-2

```

**WD-6: I can use filtering joins to filter rows from a dataframe.**

-   `semi_join()`

```{r}
#| label: wd-6-semi

```

-   `anti_join()`

```{r}
#| label: wd-6-anti

```

**WD-7: I can pivot dataframes from long to wide and visa versa**

-   `pivot_longer()`

```{r}
#| label: wd-7-long

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   `pivot_wider()`

```{r}
#| label: wd-7-wide

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

## Reproducibility

**R-1: I can create professional looking, reproducible analyses using RStudio projects, Quarto documents, and the here package.**

The following assignments satisfy the above criteria:

-   Example 1
-   Example 2
-   Example 3
-   Example 4
-   Example 5

**R-2: I can write well documented and tidy code.**

-   Example of **ggplot2** plotting

```{r}
#| label: r-2-1

# Lab 4 Problem 8

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::dollar_format()) +
  scale_y_continuous(labels = scales::dollar_format())
```

-   Example of **dplyr** pipeline

```{r}
#| label: r-2-2

# Lab 4 Problem 6

ca_childcare %>%
  filter(study_year == 2018) %>%
  group_by(census_region) %>%
  summarize(median_mc_infant = median(mc_infant), .groups = "drop") %>%
  slice_min(median_mc_infant, n = 1)

```

-   Example of function formatting

```{r}
#| label: r-2-3

```

**R-3: I can write robust programs that are resistant to changes in inputs.**

-   Example (any context)

```{r}
#| label: r-3-example

```

-   Example (function stops)

```{r}
#| label: r-3-function-stops

```

## Data Visualization & Summarization

**DVS-1: I can create visualizations for a *variety* of variable types (e.g., numeric, character, factor, date)**

-   At least two numeric variables

```{r}
#| label: dvs-1-num

# Lab 4 Problem 8

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::dollar_format()) +
  scale_y_continuous(labels = scales::dollar_format())

```

-   At least one numeric variable and one categorical variable

```{r}
#| label: dvs-2-num-cat

# Lab 2 Problem 8

ggplot(data = surveys, aes(x = species, y = weight)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(width = 0.2, color = "steelblue", alpha = 0.3) + 
  labs(
    x = "Species",
    y = "Weight (g)",
    title = "Distribution of Weight by Species"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

-   At least two categorical variables

```{r}
#| label: dvs-2-cat

```

-   Dates (time series plot)

```{r}
#| label: dvs-2-date

```

**DVS-2: I use plot modifications to make my visualization clear to the reader.**

-   I can modify my plot theme to be more readable

```{r}
#| label: dvs-2-ex-1

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   I can modify my colors to be accessible to anyone's eyes

```{r}
#| label: dvs-2-ex-2

# Lab 4 Problem 8

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::dollar_format()) +
  scale_y_continuous(labels = scales::dollar_format())

```

-   I can modify my plot titles to clearly communicate the data context

```{r}
#| label: dvs-2-ex-3

# Lab 4 Problem 8

ggplot(ca_childcare, aes(x = mhi_2018, y = mc_infant)) +
  geom_point(color = "steelblue", alpha = 0.7) +
  geom_smooth(method = "lm", color = "darkred") +
  labs(
    title = "Household Income vs. Infant Childcare Prices in California",
    x = "Median Household Income (2018 USD)",
    y = "Weekly Childcare Cost ($)"
    ) +
  scale_x_continuous(labels = scales::dollar_format()) +
  scale_y_continuous(labels = scales::dollar_format())

```

-   I can modify the text in my plot to be more readable

```{r}
#| label: dvs-2-ex-4

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   I can reorder my legend to align with the colors in my plot

```{r}
#| label: dvs-2-ex-5

```

**DVS-3: I show creativity in my visualizations**

-   I can use non-standard colors (Example 1)

```{r}
#| label: dvs-3-1-ex-1

# Challenge 2 Medium: Exploring Colors

library(viridis)

ggplot(data = surveys, aes(x = weight, y = species, fill = sex)) +
  geom_boxplot(outlier.shape = NA, position = position_dodge(width = 0.8)) +
  geom_jitter(aes(color = sex), position = position_jitterdodge(jitter.width = 0.2, dodge.width = 0.8), alpha = 0.05) +
  scale_color_viridis_d(option = "plasma", begin = 0.2, end = 0.8) +
  labs(
    x = "Weight (g)",
    y = "Species",
    title = "Distribution of Weight by Species and Sex (Flipped, Colored by Sex)"
  )

```

-   I can use non-standard colors (Example 2)

```{r}
#| label: dvs-3-1-ex-2

```

-   I can use annotations (e.g., `geom_text()`)

```{r}
#| label: dvs-3-2

```

-   I can choose creative geometries (e.g., `geom_segment()`, `geom_ribbon)()`)

```{r}
#| label: dvs-3-3

```

**DVS-4: I can calculate numerical summaries of variables.**

-   Example using `summarize()`

```{r}
#| label: dvs-4-summarize

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

-   Example using `across()`

```{r}
#| label: dvs-4-across

```

**DVS-5: I can find summaries of variables across multiple groups.**

-   Example 1

```{r}
#| label: dvs-5-16

```

-   Example 2

```{r}
#| label: dvs-5-2

# Lab 3 Problem 10

teacher_evals_clean %>%
  filter(question_no == 901) %>%
  group_by(teacher_id) %>%
  summarize(
    n_courses = n_distinct(course_id),
    avg_q1_score = mean(SET_score_avg)
  ) %>%
  filter(n_courses >= 5) %>%
  ungroup() %>%
  filter(avg_q1_score == max(avg_q1_score) | avg_q1_score == min(avg_q1_score))

```

**DVS-6: I can create tables which make my summaries clear to the reader.**

-   I can modify my column names to clearly communicate the data context

```{r}
#| label: dvs-6-ex-1

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

-   I can modify the text in my table to be more readable (e.g., bold face for column headers)

```{r}
#| label: dvs-6-ex-2

```

-   I can arrange my table to have an intuitive ordering

```{r}
#| label: dvs-6-ex-3

# Lab 4 Problem 5

ca_childcare |>
  filter(study_year %in% c(2008, 2018)) |>
  group_by(census_region, study_year) |>
  summarize(median_income_2018_dollars = median(mhi_2018), .groups = "drop") |>
  pivot_wider(
    names_from = study_year,
    names_glue = "Median_Income_{study_year}_USD",
    values_from = median_income_2018_dollars
  ) |>
arrange(desc(Median_Income_2018_USD))

```

**DVS-7: I show creativity in my tables.**

-   I can use non-default colors

```{r}
#| label: dvs-7-ex-1

```

-   I can modify the layout of my table to be more readable (e.g., `pivot_longer()` or `pivot_wider()`)

```{r}
#| label: dvs-7-ex-2

```

## Program Efficiency

**PE-1: I can write concise code which does not repeat itself.**

-   using a single function call with multiple inputs (rather than multiple function calls)

```{r}
#| label: pe-1-one-call

```

-   using `across()`

```{r}
#| label: pe-1-across

# Lab 3 Problem 5

teacher_evals_clean <- teacher_evals %>%
  rename(sex = gender) %>%
  filter(no_participants >= 10) %>%
  mutate(across(c(teacher_id, course_id), as.character),
         across(c(question_no, academic_degree, sex), as.factor)
  ) %>%
  select(course_id, teacher_id, question_no, no_participants, resp_share,
         SET_score_avg, percent_failed_cur, academic_degree, seniority, sex)
teacher_evals_clean

```

-   using functions from the `map()` family

```{r}
#| label: pe-1-map-1


```

**PE-2: I can write functions to reduce repetition in my code.**

-   Example 1: Function that operates on vectors

```{r}
#| label: pe-2-1

```

-   Example 2: Function that operates on data frames

```{r}
#| label: pe-2-2

```

-   Example 3: Function that operates on vectors *or* data frames

```{r}
#| label: pe-2-3

```

**PE-3:I can use iteration to reduce repetition in my code.**

-   using `across()`

```{r}
#| label: pe-3-across


```

-   using a `map()` function with **one** input (e.g., `map()`, `map_chr()`, `map_dbl()`, etc.)

```{r}
#| label: pe-3-map-1

```

-   using a `map()` function with **more than one** input (e.g., `map_2()` or `pmap()`)

```{r}
#| label: pe-3-map-2

```

**PE-4: I can use modern tools when carrying out my analysis.**

-   I can use functions which are not superseded or deprecated

```{r}
#| label: pe-4-1

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

-   I can connect a data wrangling pipeline into a `ggplot()`

```{r}
#| label: pe-4-2

# Lab 4 Problem 7

ca_childcare %>%
  select(census_region, study_year, mc_infant, mc_toddler, mc_preschool) %>%
  pivot_longer(
    cols = c(mc_infant, mc_toddler, mc_preschool),
    names_to = "age_group",
    values_to = "median_price"
  ) %>%
  mutate(
    age_group = factor(age_group,
                       levels = c("mc_infant", "mc_toddler", "mc_preschool"),
                       labels = c("Infant", "Toddler", "Preschool")),
    census_region = fct_reorder(census_region, median_price, .fun = median)
  ) %>%
  ggplot(aes(x = study_year, y = median_price, color = census_region)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "loess", se = FALSE) +
  facet_wrap(~ age_group, nrow = 1) +
  labs(
    title = "Weekly Median Price for Center-Based Childcare ($)",
    x = "Study Year",
    y = "Weekly Median Price",
    color = "California Region"
  ) +
  scale_x_continuous(breaks = seq(2008, 2018, by = 2)) +
  theme(
    legend.position = "right",
    aspect.ratio = 1,
    axis.text.x = element_text(size = 7, angle = 0, vjust = 0.5),
    axis.title.x = element_text(size = 9),
    plot.title = element_text(size = 10)
  )

```

## Data Simulation & Statisical Models

**DSSM-1: I can simulate data from a *variety* of probability models.**

-   Example 1

```{r}
#| label: dsm-1-1

```

-   Example 2

```{r}
#| label: dsm-1-2

```

**DSSM-2: I can conduct common statistical analyses in R.**

-   Example 1

```{r}
#| label: dsm-2-1

# Lab 4 Problem 9

reg_mod1 <- lm(mc_infant ~ mhi_2018, data = ca_childcare)
summary(reg_mod1)

```

-   Example 2

```{r}
#| label: dsm-2-2

# Lab 2 Problem 17

species_mod <- aov(weight ~ species, data = surveys)
summary(species_mod)

```

-   Example 3

```{r}
#| label: dsm-2-3

# Lab 1 Problem 10

t.test(len ~ supp,       
       data = ToothGrowth,
       var.equal = FALSE,  
       alternative = "two.sided")
```

## Revising My Thinking

<!-- How did you revise your thinking throughout the course? How did you revise your thinking on the code examples you have provided in your portfolio? -->

<!-- For the revisions included in your Portfolio, to help me understand the nature of your revisions, please denote somehow the feedback I provided you (e.g., boldface, italics, colored text) before your revisions. -->

## Extending My Thinking

<!-- How did you extended your thinking throughout the course? How did you extend your thinking on the code examples you have provided in your portfolio? -->

## Peer Support & Collaboration

<!-- Include an image or a description of feedback you gave that you are proud of (either in a peer review or in Discord). -->

<!-- Include a description of how you grew as a collaborator through the weekly pair programming activities.   -->
